---
title: "Gapminder Data Analysis Report"
author: "Wes Bickford"
date: "1/18/2017"
output: html_document
---

```{r libraries, echo=F}
library(ggplot2)
source("code/gapminder_utilities.R")
```

# My first heading of my first Document
This is the first document I have created in R markdown since 2014. Back then I did not know what I was doing at all, now I know a little more. Maybe like `r sqrt(.05)` more than before. 

### What will I get out of using R markdown?
I want to use R markdown to dhare my data and recent analyses with collaborators and PI's at the *University of Michigan* and *USGS*. 

I think it would be really cool to use markdown for whole papers, but that seems difficult. 

##### My First Table

I am going to try to creat a table. 


The number of times computer crashed 

| Me |  Jill   |
|:--:|:-------:|
| 0  | infinty |

This is an intial report describing changes in life expectancy over the past 60 years as it relates to GDP, country, and continent

```{r load_data, echo=FALSE}
gapminder <- read.csv("data/gapminder-FiveYearData.csv")
```

The gapminder dataset contains `r ncol(gapminder)` variables from `r nrow(gapminder)` observations.

```{r, facet_plot, echo=FALSE, fig.height = 3.0, fig.width = 10.5, fig.path = "figures/"}
ggplot(data=gapminder, aes(x = year, y = lifeExp, color = continent)) +
	geom_point() +
  facet_grid(.~continent)
```

```{r gdp}
calcGDP(gapminder, year= 2002, country="China")
calcGDP(gapminder, country = "China")
calcGDP(head(gapminder))
```

